Timely Object Recognition

### 2012-03-05 writeups/eccv12/evaluation.tex

\begin{figure}[h!]
\centering
\subfloat[Detection]{\includegraphics[width=0.48\linewidth]
    {figures/entropy_plots_det_avg.png}} \hfill
\subfloat[Classification]{\includegraphics[width=0.48\linewidth]
    {figures/entropy_plots_cls_whole.png}}
  \caption{Entropy reward function.}
  \label{fig:results_entropy}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
    {figures/entropy_plots_det_avg.png}} \\
\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
    {figures/entropy_plots_cls_whole.png}}
  \caption{Entropy reward function.}
  \label{fig:results_entropy}
\end{figure}
